Scheduling and Amortization for MPC

### 2022-02-11 biometric_vectorization_example.tex
Added draft of Phase 4 of Basic Vectorization (Dimensionality reduction). Still work in progress.

>>>>

\subsubsection{Phase 4 of Basic Vectorization}

And this phase gets rid of redundant dimensionality. Code moves back to 
a version close to the original one.

{\small
\begin{verbatim}
min_sum!1 = 10000
min_index!1 = 0
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))

sum!2 = [0,..,0]
d!3[I,J] = SUB_SIMD(S!0^[I,J],C!0^[I,J])
p!3[I,J] = MUL_SIMD(d!3[I,J] * d!3[I,J])

for j in range(0, D!0):
  // I dim is a noop. sum is already a one-dimensional vector
  sum!3[I] = PHI(sum!2^[I], sum!4[I])       
  sum!4[I] = ADD_SIMD(sum!3[I],p!3[I,j])

min_index!3 = [0,1,...N!0-1]

for i in range(0, N!0):
  min_sum!2 = PHI(min_sum!1, min_sum!4) 
  !1!2[i] = CMP(sum!3[i],min_sum!2)
  min_sum!4 = MUX(!1!2[i], sum!3[i], min_sum!2)

for i in range(0, N!0):
  min_index!2 = PHI(min_index!1, min_index!4)  
  min_index!4 = MUX(!1!2[i], min_index!3[i], min_index!2)

!2!1 = (min_sum!2, min_index!2)   
\end{verbatim}
}

### 2022-02-11 paper_SIMD.tex
Added draft of Phase 4 of Basic Vectorization (Dimensionality reduction). Still work in progress.

>>>>

\COMMENT {Phase 4: Dimensionality reduction: remove unnecessary dimensionality. \ana{Draft. Needs work.}}
\FOR {each FOR i = 0; ... loop from innermost to outermost}
\FOR {each stmt v[...i...] = ..., including in nested loops}
\STATE {if def-use from stmt v[...i...] to a non drop\_dim(v,i) use outside of loop, mark "live dimension i"}
\STATE {otherwise, mark "dead dimension i"}
\STATE {for all variables v[...i...] (defs and uses) that are "dead dimension i", remove dimension i}
\COMMENT {Two cases: forward edge will use i, backward edge will use i-1}
\ENDFOR

\COMMENT {Now clean up drop\_dim and raise\_dim}
\FOR {each "dead dimension i" def: v[...i...] in loop to use: v' =  drop\_dim(v,i) }
\STATE {replace v' = drop\_dim(v,i) with v' = v in use}
\ENDFOR
\FOR {each "def: v' = raise\_dim(v,i) in outer loop to use: v'[...i...] in loop}
\STATE {replace v' with v in use statement}
\ENDFOR
\ENDFOR
\STATE {do copy propagation and dead code elimination to get rid of redundant variables and raise dimension statements}
